Predicting tree failure likelihood for utility risk mitigation via artificial intelligence

### 2021-03-04 docs/manuscript/manuscript.tex
generated images for figure 2

\begin{figure}[ht]
  \centering
  \begin{subfigure}[t]{.32\linewidth}\centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{probable-example-1} %probable_standing dead.JPG

    \includegraphics[width=\textwidth,keepaspectratio=true]{probable-example-2} %Probable (deadwood above line hieght, vine)
    \caption{Probable}
  \end{subfigure}
  \begin{subfigure}[t]{.32\linewidth}\centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{possible-example-1} % Possible (spruce, codominant and dieback)

    \includegraphics[width=\textwidth,keepaspectratio=true]{possible-example-2} % Possible (silver maple, codom weak attach, reaction wood)
    \caption{Possible}   
  \end{subfigure}
  \begin{subfigure}[t]{.32\linewidth}\centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{improbable-example-1} %Improbable_3_london plane

    \includegraphics[width=\textwidth,keepaspectratio=true]{improbable-example-2}
    \caption{Improbable}
  \end{subfigure}
  \caption{Examples of training images in each of the three tree risk categories considered in this study.
  Trees in the right-hand column were categorized as improbable due to their lack of structural defects as well as good physiological health. Trees in the center column were categorized as possible due to weak branch unions and crown dieback. Trees in the left-hand column were categorized as probable because they were dead. Leaves in the bottom image in the left-hand column are from vines attached to the dead tree. Images are antialiased in this figure for greater clarity}
  \label{fig:raw_images}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
  \begin{subfigure}[t]{.32\linewidth}\centering
    \includegraphics[width=\textwidth,keepaspectratio=true,angle=-90]{probable-example-1} %probable_standing dead.JPG

    \includegraphics[width=\textwidth,keepaspectratio=true,angle=-90]{probable-example-2} %Probable (deadwood above line hieght, vine)
    \caption{Probable}
  \end{subfigure}
  \begin{subfigure}[t]{.32\linewidth}\centering
    \includegraphics[width=\textwidth,keepaspectratio=true,angle=-90]{possible-example-1} % Possible (spruce, codominant and dieback)

    \includegraphics[width=\textwidth,keepaspectratio=true,angle=-90]{possible-example-2} % Possible (silver maple, codom weak attach, reaction wood)
    \caption{Possible}   
  \end{subfigure}
  \begin{subfigure}[t]{.32\linewidth}\centering
    \includegraphics[width=\textwidth,keepaspectratio=true,angle=-90]{improbable-example-1} %Improbable_3_london plane

    \includegraphics[width=\textwidth,keepaspectratio=true,angle=-90]{improbable-example-2}
    \caption{Improbable}
  \end{subfigure}
  \caption{Examples of training images in each of the three tree risk categories considered in this study.
  Trees in the right-hand column were categorized as improbable due to their lack of structural defects as well as good physiological health. Trees in the center column were categorized as possible due to weak branch unions and crown dieback. Trees in the left-hand column were categorized as probable because they were dead. Leaves in the bottom image in the left-hand column are from vines attached to the dead tree. Images are antialiased in this figure for greater clarity}
  \label{fig:raw_images}
\end{figure}
